\LARGE Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-13 TPDP2018/poster/main.tex
update the prior plots
size adjust

  \item {\textbf{\color{blue}{Blue}}}: $\hexpmech$. The fact that there is only one candidate distribution which achieves the highest score and different
    distributions which achieve a sub-optimal score explains the (highest) peaks in Fig.  \ref{subfig_concrete_prob_2d} (and Fig. \ref{subfig_concrete_prob_3d}).
\end{itemize}
% In Fig. \ref{subfig_concrete_prob_2d} and \ref{subfig_concrete_prob_3d} we plot on the x-axis the Hellinger distance from the true posterior and on the y-axis the
% probability of the distributions with that distance under the different mechanisms. In Fig. \ref{subfig_prior} we present the influence of the prior on the accuracy of the three mechanisms,
% by showing the quartiles of the experimental distribution of the Hellinger distance.
\begin{figure}[H]
\begin{center}
\centering
  \subfigure[2 dimensions with data size $600$]{
    \includegraphics[width=0.31\textwidth]{poster_5.eps}
  \label{subfig_concrete_prob_2d}
  }
  \subfigure[3 dimensions with data size $600$]{
    \includegraphics[width=0.31\textwidth]{poster_6.eps}
  \label{subfig_concrete_prob_3d}
  } 
\subfigure[2 dimensions with data size $100$]{
    \includegraphics[width=0.31\textwidth]{poster_6.eps}
  \label{subfig_prior}
  }

  % \subfigure[\footnotesize{2 dimensions, data size $\in [100,500]$}]{
  %   \includegraphics[width=0.333\textwidth]{poster_1.eps}
  %   \label{subfig_sampling_2d}
  % }

  \subfigure[2 dimensions with data size $100$]{
    \includegraphics[width=0.314\textwidth]{poster_4.eps}
  \label{subfig_prior}
  }
  \subfigure[\footnotesize{3 dimensions, data size $\in [100,500]$} ]{
    \includegraphics[width=0.31\textwidth]{poster_2.eps}
  \label{subfig_sampling_3d}
  } 
  \subfigure[\footnotesize{4 dimensions, data size $\in [100,600]$}]{
    \includegraphics[width=0.304\textwidth]{poster_3.eps}
    \label{subfig_sampling_4d}
  }
  \caption{Priors are $\betad(1,1), \dirichlet(1,1,1)$ and $\dirichlet(1,1,1,1)$ (except for Figure \ref{subfig_prior}) ,
    balanced datasets, $\epsilon = 1.0$ and $\delta = 10^{-8}$. }
\label{fig_sampling}
\end{center}

>>>>

  \item {\textbf{\color{blue}{Blue}}}: $\hexpmech$. The fact that there is only one candidate distribution which achieves the highest score and different
    distributions which achieve a sub-optimal score explains the (highest) peaks in Fig.  \ref{subfig_concrete_prob_2d} (and Fig. \ref{subfig_concrete_prob_3d}).
\end{itemize}
% In Fig. \ref{subfig_concrete_prob_2d} and \ref{subfig_concrete_prob_3d} we plot on the x-axis the Hellinger distance from the true posterior and on the y-axis the
% probability of the distributions with that distance under the different mechanisms. In Fig. \ref{subfig_prior} we present the influence of the prior on the accuracy of the three mechanisms,
% by showing the quartiles of the experimental distribution of the Hellinger distance.
\begin{figure}[H]
\begin{center}
\centering
  \subfigure[2 dimensions with data size $600$]{
    \includegraphics[width=0.312\textwidth]{poster_5.eps}
  \label{subfig_concrete_prob_2d}
  }
  \subfigure[3 dimensions with data size $600$]{
    \includegraphics[width=0.312\textwidth]{poster_6.eps}
  \label{subfig_concrete_prob_3d}
  } 
\subfigure[2 dimensions with data size $100$]{
    \includegraphics[width=0.308\textwidth]{poster_4.eps}
  \label{subfig_prior}
  }

  \subfigure[\footnotesize{2 dimensions, data size $\in [100,500]$}]{
    \includegraphics[width=0.333\textwidth]{poster_1.eps}
    \label{subfig_sampling_2d}
  }
  % \subfigure[2 dimensions with data size $100$]{
  %   \includegraphics[width=0.314\textwidth]{poster_4.eps}
  % \label{subfig_prior}
  % }
  \subfigure[\footnotesize{3 dimensions, data size $\in [100,500]$} ]{
    \includegraphics[width=0.301\textwidth]{poster_2.eps}
  \label{subfig_sampling_3d}
  } 
  \subfigure[\footnotesize{4 dimensions, data size $\in [100,600]$}]{
    \includegraphics[width=0.294\textwidth]{poster_3.eps}
    \label{subfig_sampling_4d}
  }
  \caption{{\footnotesize Priors are $\betad(1,1), \dirichlet(1,1,1)$ and $\dirichlet(1,1,1,1)$ (except for Figure \ref{subfig_prior}) ,
      balanced datasets, $\epsilon = 1.0$ and $\delta = 10^{-8}$. }}
\label{fig_sampling}
\end{center}
